Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition.

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
more refs to RNN for DAR

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
% TODO: RNN with attention: \citep{bothe2018conversational,zhao2018unified}

>>>>

Most successful neural approaches also model some notion of context.
We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
